A Rapid Feasibility Checking for Reconfiguration of Mismatched PV Arrays

### 2019-06-01 PVSC-46/Manuscript/PVSC_Manuscript.tex
Updates from Overleaf

For the method in \cite{orozco2016optimized}, first, close values \michiko{of extracted currents or voltages are} approximated and grouped into a small number of classes so that the number of possible combinations, or a search space, is reduced.
Then possible combinations of reconfiguration are enumerated.
For each candidate configuration \michiko{its generated} power value \michiko{is} estimated by \cite{orozco2015fast} along with careful estimation of possible errors.
For example, Table \ref{tab:monitored} shows extracted currents for 4 panels each of which has 3 modules, and they are approximated into four current levels as shown in Table \ref{tab:approximated}. 
% Then currents and voltages of MPPs are approximated and grouped into a small number of classes so that the number of possible combinations, or a search space, is reduced.
As mentioned in Section \ref{Sec2}, if some panel has $m$ MPPs with current level of $I$ or larger, $m$ modules can be active with current level of $I$. 
Table \ref{tab:modules} shows the maximum number of active modules for each current level.
Control voltage for one PV model is approximated to 20V.
Approximated power values for possible configurations are shown in Table \ref{tab:powers}. 
% Then power values are approximated for possible configurations. 
Table \ref{tab:powers} shows an example to form a PV array with two strings,
%where power value is simply multiplied PV array current with control voltage .
\michiko{where control voltages are approximated as multiples of 20V (the number of active modules per string times 20V), and power values of strings are obtained as products of current and voltage values.) For example, when current levels of two strings are 3A and 2.5A and the number of active modules per string is 3, the control voltage is 60V, and two strings generate powers of $3\mbox{A} \times 60\mbox{V} = 180\mbox{W}$ and $2.5\mbox{A} \times 60\mbox{A} = 150\mbox{W}$, and the total generated power is 330W.}

\michiko{When constructing an approximated power matrix like Table~\ref{tab:powers}, the possibility that an array can be formed for given a current sequence and the number of active modules per string (it is called \textit{feasibility}) is examined.}
The method \michiko{provides} a simple feasibility check as follows.

>>>>

For the method in \cite{orozco2016optimized}, first, close values \michiko{of extracted currents or voltages are} approximated and grouped into a small number of classes so that the number of possible combinations, or a search space, is reduced.
Then possible combinations of reconfiguration are enumerated.
For each candidate configuration \michiko{its generated} power value \michiko{is} estimated by \cite{orozco2015fast} along with careful estimation of possible errors.
For example, Table \ref{tab:monitored} shows extracted currents for 4 panels each of which has 3 modules, and they are approximated into four current levels as shown in Table \ref{tab:approximated}. 
% Then currents and voltages of MPPs are approximated and grouped into a small number of classes so that the number of possible combinations, or a search space, is reduced.
As mentioned in Section \ref{Sec2}, if some panel has $m$ MPPs with current level of $I$ or larger, $m$ modules can be active with current level of $I$. 
Table \ref{tab:modules} shows the maximum number of active modules for each current level.
Control voltage for one PV model is approximated to 20V.
Approximated power values for possible configurations are shown in Table \ref{tab:powers}. 
% Then power values are approximated for possible configurations. 
Table \ref{tab:powers} shows an example to form a PV array with two strings,
%where power value is simply multiplied PV array current with control voltage .
\michiko{where control voltages are approximated as multiples of 20V (the number of active modules per string times 20V), and power values of strings are obtained as products of current and voltage values. For example, when current levels of two strings are 3A and 2.5A and the number of active modules per string is 3, the control voltage is 60V, and two strings generate powers of $3\mbox{A} \times 60\mbox{V} = 180\mbox{W}$ and $2.5\mbox{A} \times 60\mbox{A} = 150\mbox{W}$, and the total generated power is 330W.}

\michiko{When constructing an approximated power matrix like Table~\ref{tab:powers}, the possibility that an array can be formed for a given current sequence and the number of active modules per string (it is called \textit{feasibility}) is examined.}
The method \michiko{provides} a simple feasibility check as follows.
